A search method for Gaussian mixtures using MML

### 2017-10-11 ms.tex
Update on Overleaf.

@@

And, of course, one could change K from 2 to something bigger.

There should still be some use of randomness in the search.
\bibliographystyle{elsarticle-num}
\bibliography{mmlbibliography}

>>>>

\section{Related Work in Inferring the Number of Mixture Components}

Akaike information criterion (AIC) ~\cite{akaike1974} chooses a model that minimizes the Kullback-Leibler distance between the model and the truth, defined as:

AIC = -2 (ln ( likelihood )) + 2 K

where likelihood is the probability of the data given a model and K is the number of free parameters in the model.

BIC

@@

\bibliographystyle{elsarticle-num}
\bibliography{mmlbibliography}
